## How do I select client's most recent assessment, and the one closest to a year prior?

Firt, we will create a sample data set.

```{r selecting assessments a year before - create data}
library(dplyr)
library(tidyr)

# Loading your data into a data frame in R
df <- data.frame(ANSA = 1:6,
                 ID = c(1, 1, 2, 3, 3, 3),
                 ANSA_Date = as.Date(c("2017-1-1", "2012-5-20", "2017-1-1", "2017-1-1", "2016-1-25", "2015-9-30")))


```

Next, group the rows by client ID, and creating a series of columns which identify which is most recent, how long ago the others are, and which is closest to 365 days before the most recent.

```{r selecting assessments a year before - create indicators}

df_calcs <-
  df %>%
  group_by(ID) %>%
  mutate(mostRecentDate = max(ANSA_Date),
         isMostRecent = ANSA_Date == mostRecentDate,
         timeToRecent = mostRecentDate - ANSA_Date,
         timeToYearPrior = abs(timeToRecent - 365))
df_calcs
```

Subset the rows to keep only the most recent, or the assessment whose timing is the minimum time to the prior year.

```{r selecting assessments a year before - subset rows}
df_sub <- 
  df_calcs %>%
  filter(isMostRecent | timeToYearPrior == min(timeToYearPrior))
df_sub
```

Finally, selecting only the fields that we want.

```{r selecting assessments a year before - preserve only desired fields}

df_final <-
  df_sub %>%
  select(ANSA, ID, ANSA_Date)
df_final
```

